Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-12-01 edubots_surveys.Rnw
Fixes caption

    \caption{Use of chatbots provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}

>>>>

    \caption{Use of \textcolor{blue}{messaging platforms either external or} provided by the teachers' academic institutions in class: distributions per gender, years of experience in education, university or vocational education, and discipline.}
